### 2010-09-20 doc/manuals/hopi/hopi-manual.tex
Synchronising Echo and Hopi documentation with Nox
Assigning a number to Hopi manual
Switching documents to bibliography style which is supposed to be present in latex distributions. Fixes in some documents and build procedures.
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Zsombor Nagy},
  pdftitle = {The Hopi service},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

{\raggedleft NORDUGRID-MANUAL-XXX\par}

@@

\begin{verbatim}
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
	xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
	xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
	xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08">
    <cfg:Server>
        <cfg:PidFile>tmp/arched.pid</cfg:PidFile>
        <cfg:Logger>
            <cfg:File>/var/log/arched.log</cfg:File>
            <cfg:Level>ERROR</cfg:Level>
        </cfg:Logger>
    </cfg:Server>
    <ModuleManager>
        <Path>/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins>
        <Name>mcctls</Name>
        <Name>mcchttp</Name>
        <Name>mccsoap</Name>
        <Name>mcctcp</Name>
    </Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/>
            <tcp:Listen>
                <tcp:Interface>0.0.0.0</tcp:Interface>
                <tcp:Port>50000</tcp:Port>
                <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
            <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
            <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
            <next id="plexer">GET</next>
            <next id="plexer">PUT</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="hopi">^/hopi/</next>
        </Plexer>
        <Service name="hopi" id="hopi">
            <DocumentRoot>/tmp/hopi</DocumentRoot>
            <SlaveMode>0</SlaveMode>
        </Service>
    </Chain>
</cfg:ArcConfig>
\end{verbatim}
% section configuration (end)

>>>>

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Zsombor Nagy},
  pdftitle = {The Hopi service},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

{\raggedleft NORDUGRID-MANUAL-15\par}

@@

\begin{verbatim}
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
	xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
	xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
	xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08">
    <cfg:Server>
        <cfg:PidFile>tmp/arched.pid</cfg:PidFile>
        <cfg:Logger>
            <cfg:File>/var/log/arc/arched.log</cfg:File>
            <cfg:Level>ERROR</cfg:Level>
        </cfg:Logger>
    </cfg:Server>
    <ModuleManager>
        <Path>/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins>
        <Name>mcctls</Name>
        <Name>mcchttp</Name>
        <Name>mccsoap</Name>
        <Name>mcctcp</Name>
    </Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/>
            <tcp:Listen>
                <tcp:Interface>0.0.0.0</tcp:Interface>
                <tcp:Port>50000</tcp:Port>
                <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
            <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
            <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
            <next id="plexer">GET</next>
            <next id="plexer">PUT</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="hopi">^/hopi/</next>
        </Plexer>
        <Service name="hopi" id="hopi">
            <DocumentRoot>/tmp/hopi</DocumentRoot>
            <SlaveMode>0</SlaveMode>
        </Service>
    </Chain>
</cfg:ArcConfig>
\end{verbatim}
% section configuration (end)

### 2010-09-20 doc/manuals/janitor/tex_installation/installation.tex
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/

log4perl.appender.MainLog = Log::Log4perl::Appender::File
log4perl.appender.MainLog.Threshold = DEBUG
log4perl.appender.MainLog.filename = /var/log/janitor.log
log4perl.appender.MainLog.layout = PatternLayout
log4perl.appender.MainLog.layout.ConversionPattern = %d %p> %m%n

log4perl.appender.ErrorLog = Log::Log4perl::Appender::File
log4perl.appender.ErrorLog.Threshold = ERROR
log4perl.appender.ErrorLog.filename = /var/log/janitor_error.log

>>>>

log4perl.appender.MainLog = Log::Log4perl::Appender::File
log4perl.appender.MainLog.Threshold = DEBUG
log4perl.appender.MainLog.filename = /var/log/arc/janitor.log
log4perl.appender.MainLog.layout = PatternLayout
log4perl.appender.MainLog.layout.ConversionPattern = %d %p> %m%n

log4perl.appender.ErrorLog = Log::Log4perl::Appender::File
log4perl.appender.ErrorLog.Threshold = ERROR
log4perl.appender.ErrorLog.filename = /var/log/arc/janitor_error.log

### 2010-09-20 doc/tech_doc/a-rex/arex_tech_doc.tex
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/

\begin{itemize}
\item \textbf{\textit{pidfile}}\textit{=path} -- specifies file where
  process id of A-REX process will be stored. Defaults to
  \emph{/var/log/arched.pid} if running as root and
  \emph{\$HOME/arched.pid} otherwise.
\item \textbf{\textit{logfile}}\textit{=path} -- specifies name of file
  for logging debug/informational output. Defaults to
  \emph{/var/log/grid-manager.log}.
\item \textbf{\textit{logsize}}\textit{=size number} -- restricts
  log file size to \emph{size} and keeps \emph{number} archived log
  files.
\item \textbf{\textit{debug}}\textit{=number} -- specifies level of
  debug information. More information is printed for higher
  levels. Currently the highest effective number is 5 (DEBUG) and
  lowest 0 (FATAL). Defaults to 2 (WARNING).
\item \textbf{\textit{user}}\textit{=username} -- specifies username to
  which the A-REX must switch after reading configuration. Defaults to
  \emph{not switch}.
\end{itemize}

@@

\begin{shaded}
\begin{verbatim}
<?xml version="1.0"?>
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/arcconfig/2009/08"
  xmlns:loader="http://www.nordugrid.org/schemas/loader/2009/08"
  xmlns:arex="http://www.nordugrid.org/schemas/a-rex/2009/08"
  xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
  xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
  xmlns:authz="http://www.nordugrid.org/schemas/arcauthz/2009/08"
  xmlns:idmap="http://www.nordugrid.org/schemas/identitymap/2009/10"
>
  <!-- Common configuration of the daemon -->
  <Server>
    <PidFile>/var/run/arched.pid</PidFile>
    <Logger>
      <Level>VERBOSE</Level>
      <File>/var/log/arched.log</File>
      <MaxSize>100000000</MaxSize>
      <Backups>10</Backups>
    </Logger>
  </Server>
  <!-- Where to find plugins -->
  <loader:ModuleManager>
    <loader:Path>/usr/local/lib/arc/</loader:Path>
  </loader:ModuleManager>
  <!-- Simply load all needed plugins -->
  <loader:Plugins>
    <loader:Name>mcctcp</loader:Name>
    <loader:Name>mcctls</loader:Name>
    <loader:Name>mcchttp</loader:Name>
    <loader:Name>mccsoap</loader:Name>
    <loader:Name>arcpdc</loader:Name>
    <loader:Name>identitymap</loader:Name>
    <loader:Name>arex</loader:Name>
  </loader:Plugins>
  <!-- Create a chain -->
  <loader:Chain>
    <!-- TCP listening socket -->
    <loader:Component name="tcp.service" id="tcp">
      <loader:next id="tls"/>
      <tcp:Listen><tcp:Port>60000</tcp:Port></tcp:Listen>
    </loader:Component>
    <!-- Transport-level security -->
    <loader:Component name="tls.service" id="tls">
      <loader:next id="http"/>
      <!-- Location of server's security keys -->
      <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
      <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
      <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
      <!-- Evaluate requestor's identity into local identity.
      Comment it if no user mapping is needed. -->
      <loader:SecHandler name="identity.map" id="map" event="incoming">
        <!-- Safe choice if all other rules failed -->
        <idmap:PDP name="allow.pdp"><idmap:LocalName>nobody</idmap:LocalName></idmap:PDP>
      </loader:SecHandler>
    </loader:Component>
    <!-- HTTP processing is done here -->
    <loader:Component name="http.service" id="http">
      <loader:next id="soap">POST</loader:next>
      <loader:next id="plexer">GET</loader:next>
      <loader:next id="plexer">PUT</loader:next>
    </loader:Component>
    <!-- This one parses content into XML tree -->
    <loader:Component name="soap.service" id="soap">
      <loader:next id="plexer"/>
    </loader:Component>
    <!-- Directing messages to proper service -->
    <loader:Plexer name="plexer.service" id="plexer">
      <!-- RegExp pattern is matched to path part of endpoint.
      Unmatched part of path is propagated to service in
      PLEXER:EXTENSION attribute. -->
      <loader:next id="a-rex">^/arex</loader:next>
    </loader:Plexer>
    <!-- A-Rex service -->
    <loader:Service name="a-rex" id="a-rex">
      <!-- Optional endpoint element is advised in case of multiple IP adresses -->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-- Use information generated by identity.map plugin or default provided below -->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-- grid-manager part of a-rex requires legacy configuration file.
      Use arc.conf example or write own. -->
      <arex:gmconfig>/etc/arc.conf</arex:gmconfig>
    </loader:Service>
  </loader:Chain>
</ArcConfig>
\end{verbatim}
\end{shaded}

>>>>

\begin{itemize}
\item \textbf{\textit{pidfile}}\textit{=path} -- specifies file where
  process id of A-REX process will be stored. Defaults to
  \emph{/var/log/arched.pid} if running as root and
  \emph{\$HOME/arched.pid} otherwise.
\item \textbf{\textit{logfile}}\textit{=path} -- specifies name of file
  for logging debug/informational output. Defaults to
  \emph{/var/log/arc/grid-manager.log}. If installed from packages, the
  default log is managed by logrotate.
\item \textbf{\textit{logsize}}\textit{=size number} -- restricts
  log file size to \emph{size} and keeps \emph{number} archived log
  files.
\item \textbf{\textit{debug}}\textit{=number} -- specifies level of
  debug information. More information is printed for higher
  levels. Currently the highest effective number is 5 (DEBUG) and
  lowest 0 (FATAL). Defaults to 2 (WARNING).
\item \textbf{\textit{user}}\textit{=username} -- specifies username to
  which the A-REX must switch after reading configuration. Defaults to
  \emph{not switch}.
\end{itemize}

@@

\begin{shaded}
\begin{verbatim}
<?xml version="1.0"?>
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/arcconfig/2009/08"
  xmlns:loader="http://www.nordugrid.org/schemas/loader/2009/08"
  xmlns:arex="http://www.nordugrid.org/schemas/a-rex/2009/08"
  xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
  xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
  xmlns:authz="http://www.nordugrid.org/schemas/arcauthz/2009/08"
  xmlns:idmap="http://www.nordugrid.org/schemas/identitymap/2009/10"
>
  <!-- Common configuration of the daemon -->
  <Server>
    <PidFile>/var/run/arched.pid</PidFile>
    <Logger>
      <Level>VERBOSE</Level>
      <File>/var/log/arc/arched.log</File>
      <MaxSize>100000000</MaxSize>
      <Backups>10</Backups>
    </Logger>
  </Server>
  <!-- Where to find plugins -->
  <loader:ModuleManager>
    <loader:Path>/usr/local/lib/arc/</loader:Path>
  </loader:ModuleManager>
  <!-- Simply load all needed plugins -->
  <loader:Plugins>
    <loader:Name>mcctcp</loader:Name>
    <loader:Name>mcctls</loader:Name>
    <loader:Name>mcchttp</loader:Name>
    <loader:Name>mccsoap</loader:Name>
    <loader:Name>arcpdc</loader:Name>
    <loader:Name>identitymap</loader:Name>
    <loader:Name>arex</loader:Name>
  </loader:Plugins>
  <!-- Create a chain -->
  <loader:Chain>
    <!-- TCP listening socket -->
    <loader:Component name="tcp.service" id="tcp">
      <loader:next id="tls"/>
      <tcp:Listen><tcp:Port>60000</tcp:Port></tcp:Listen>
    </loader:Component>
    <!-- Transport-level security -->
    <loader:Component name="tls.service" id="tls">
      <loader:next id="http"/>
      <!-- Location of server's security keys -->
      <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
      <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
      <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
      <!-- Evaluate requestor's identity into local identity.
      Comment it if no user mapping is needed. -->
      <loader:SecHandler name="identity.map" id="map" event="incoming">
        <!-- Safe choice if all other rules failed -->
        <idmap:PDP name="allow.pdp"><idmap:LocalName>nobody</idmap:LocalName></idmap:PDP>
      </loader:SecHandler>
    </loader:Component>
    <!-- HTTP processing is done here -->
    <loader:Component name="http.service" id="http">
      <loader:next id="soap">POST</loader:next>
      <loader:next id="plexer">GET</loader:next>
      <loader:next id="plexer">PUT</loader:next>
    </loader:Component>
    <!-- This one parses content into XML tree -->
    <loader:Component name="soap.service" id="soap">
      <loader:next id="plexer"/>
    </loader:Component>
    <!-- Directing messages to proper service -->
    <loader:Plexer name="plexer.service" id="plexer">
      <!-- RegExp pattern is matched to path part of endpoint.
      Unmatched part of path is propagated to service in
      PLEXER:EXTENSION attribute. -->
      <loader:next id="a-rex">^/arex</loader:next>
    </loader:Plexer>
    <!-- A-Rex service -->
    <loader:Service name="a-rex" id="a-rex">
      <!-- Optional endpoint element is advised in case of multiple IP adresses -->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-- Use information generated by identity.map plugin or default provided below -->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-- grid-manager part of a-rex requires legacy configuration file.
      Use arc.conf example or write own. -->
      <arex:gmconfig>/etc/arc.conf</arex:gmconfig>
    </loader:Service>
  </loader:Chain>
</ArcConfig>
\end{verbatim}
\end{shaded}

### 2010-09-20 doc/tech_doc/gridftpd/gridftpd.tex
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/

\begin{itemize}
\item \textbf{\textit{pidfile}}\textit{=path} -- specifies file where
  process id of the gridftpd process will be stored. Defaults to
  \emph{/var/run/gridftpd.pid} if running as root and
  \emph{\$HOME/gridftpd.pid} otherwise.
\item \textbf{\textit{logfile}}\textit{=path} -- specifies name of file
  for logging debug/informational output. Defaults to
  \emph{/var/log/gridftpd.log}.
\item \textbf{\textit{logsize}}\textit{=size number} -- restricts
  log file size to \emph{size} and keeps \emph{number} archived log
  files.
\item \textbf{\textit{debug}}\textit{=number} -- specifies level of
  debug information. More information is printed for higher
  levels. Currently the highest effective number is 5 (DEBUG) and
  lowest 0 (FATAL). Defaults to 3 (INFO).
\item \textbf{\textit{port}}\textit{=number} - specifies TCP/IP port
  number.  Default is 2811.
\item \textbf{\textit{include}}\textit{=path} - include contents of
  another file. Generic commands cannot be specified there.
\item \textbf{\textit{encryption}}\textit{=yes|no} - specifies if
  server will allow data transfer to be encrypted. Default is yes.
\item \textbf{\textit{pluginpath}}\textit{=path} - specifies the path
  where plugin libraries are installed. In a normal installation this
  is \emph{\$(ARC\_LOCATION)/lib/arc}.
\item \textbf{\textit{allowunknown}}\textit{=yes|no} - if set to
  \emph{yes}, clients are not checked against the grid-mapfile. Hence
  only access rules specified in this configuration file will be
  applied.
\item \textbf{\textit{firewall}}\textit{=hostname} - use IP address of
  the \textit{hostname} in response to PASV command instead of IP
  address of a network interface of the computer. An IP address can be
  used instead of \textit{hostname}. This command may be useful if the
  server is situated behind a NAT.
\item \textbf{\textit{unixgroup}}\textit{=group rule} - define local
  UNIX user and optionally UNIX group to which user belonging to
  specified authorization \textit{group} is mapped (see
  Section~\ref{sec:Authorization} for definition of group). Local
  names are obtained from the specified \textit{rule}. If the
  specified rule could not produce any mapping, the next command is
  used. Mapping stops at first matched rule. The following rules are
  supported:

@@

[gridftpd]
debug="3"
logfile="/var/log/gridftpd.log"
logsize="10000000 2"
pidfile="/var/run/gridftpd.pid"
pluginpath="/usr/local/lib/arc"
encryption="no"
allowunknown="no"
maxconnections="200"

@@

[gridftpd]
debug="2"
logfile="/var/log/gridftpd.log"
logsize="100000 2"
pidfile="/var/run/gridftpd.pid"
port="2811"
pluginpath="/usr/local/lib/arc"
encryption="no"

>>>>

\begin{itemize}
\item \textbf{\textit{pidfile}}\textit{=path} -- specifies file where
  process id of the gridftpd process will be stored. Defaults to
  \emph{/var/run/gridftpd.pid} if running as root and
  \emph{\$HOME/gridftpd.pid} otherwise.
\item \textbf{\textit{logfile}}\textit{=path} -- specifies name of file
  for logging debug/informational output. Defaults to
  \emph{/var/log/arc/gridftpd.log}. If installed from packages, the
  default log is managed by logrotate.
\item \textbf{\textit{logsize}}\textit{=size number} -- restricts
  log file size to \emph{size} and keeps \emph{number} archived log
  files.
\item \textbf{\textit{debug}}\textit{=number} -- specifies level of
  debug information. More information is printed for higher
  levels. Currently the highest effective number is 5 (DEBUG) and
  lowest 0 (FATAL). Defaults to 3 (INFO).
\item \textbf{\textit{port}}\textit{=number} - specifies TCP/IP port
  number.  Default is 2811.
\item \textbf{\textit{include}}\textit{=path} - include contents of
  another file. Generic commands cannot be specified there.
\item \textbf{\textit{encryption}}\textit{=yes|no} - specifies if
  server will allow data transfer to be encrypted. Default is yes.
\item \textbf{\textit{pluginpath}}\textit{=path} - specifies the path
  where plugin libraries are installed. In a normal installation this
  is \emph{\$(ARC\_LOCATION)/lib/arc}.
\item \textbf{\textit{allowunknown}}\textit{=yes|no} - if set to
  \emph{yes}, clients are not checked against the grid-mapfile. Hence
  only access rules specified in this configuration file will be
  applied.
\item \textbf{\textit{firewall}}\textit{=hostname} - use IP address of
  the \textit{hostname} in response to PASV command instead of IP
  address of a network interface of the computer. An IP address can be
  used instead of \textit{hostname}. This command may be useful if the
  server is situated behind a NAT.
\item \textbf{\textit{unixgroup}}\textit{=group rule} - define local
  UNIX user and optionally UNIX group to which user belonging to
  specified authorization \textit{group} is mapped (see
  Section~\ref{sec:Authorization} for definition of group). Local
  names are obtained from the specified \textit{rule}. If the
  specified rule could not produce any mapping, the next command is
  used. Mapping stops at first matched rule. The following rules are
  supported:

@@

[gridftpd]
debug="3"
logfile="/var/log/arc/gridftpd.log"
logsize="10000000 2"
pidfile="/var/run/gridftpd.pid"
pluginpath="/usr/local/lib/arc"
encryption="no"
allowunknown="no"
maxconnections="200"

@@

[gridftpd]
debug="2"
logfile="/var/log/arc/gridftpd.log"
logsize="10000000 2"
pidfile="/var/run/gridftpd.pid"
port="2811"
pluginpath="/usr/local/lib/arc"
encryption="no"

### 2010-09-20 doc/tutorials/ws-programming-tutorial/doc/tex_introduction/introduction.tex
Reorganizing doc catalogue and enabling make doc
Added a modified doc folder refering to the new folder structure of the examples
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/

\subsection{The ARC Echo Web Service}

@@

\lstsetARCHEDXML
\lstinputlisting
	[label=lst:arched_arcecho_xml,float=htb,
	caption={[HED configuration file.]
	\textbf{HED configuration file.}}]
{../src/services/arched_arcecho.xml}
The first line of the XML file contains the XML declaration.
Several attributes can be defined here but at least the XML version should be specified.
The configuration as a whole is encapsulated by the element \textit{ArcConfig}. It also performs the setting of namespaces, which are expected to be mostly invariant across all server installations. % ABBREVIATIONS?? - MG
The \textit{Server} element, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as the location of the Pid-file or ofthe Log-file.
The \textit{ModuleManager} holds the \textit{path} to the plugin libraries.
Several paths may be defined here.
Due to the fact that the first library matching the plugin name is loaded, the order is relevant.
The path should be at least assigned to the ARC installation directory.
Otherwise, the set of ARC MCC plugins might not be found.
The next elements are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the names of the dynamic libraries within the path defined in the \textit{ModuleManager}.
Finally, the chain, which creates the layered structure, is declared within the element \textit{Chain}.
It is composed of the elements \textit{Component}, \textit{Plexer} and \textit{Service}.
Due to a MCC plugin may contain several components, one has to specify more exact which one to load. This is to be done using the \textit{name} attribute i.e. the plugin \textit{mcchttp} realises two components: \textit{http.service} and \textit{http.client}. Since we are defining a configuration file for a service, the \textit{http.service} should be used.
Furthermore the elements may have the attribute \textit{id} as a unique identifier within the file.
Regarding the components and the services a plugin (implemented as a *.so file that is searched in the paths previously specified) has to be loaded which provides the implementation of its functionality. The further configuration depends on the plugin's individual functionality.\\
%
% within the chain ... 3 types of elements
%
%Its needed to distinguish between the plugins and the components.
%The plugins refer to shared libraries that can be integrated as modules with the HED to extend its functionality.
%The Components refer to the implementation of Web Services within any of those libraries.

@@

% $ rm -f /var/log/arched.log
% $ tail -n100 -f /var/log/arched.log
%...
%$ killall arched
%
%
The name of the program is followed by the parameter \textit{-c}.
The string following that argument contains the path to the configuration file.
Once the server is running, the client can be used as described in Listing~\ref{lst:arcecho_client_invokation}.
\lstsetKSH
\begin{lstlisting}[
label=lst:arcecho_client_invokation,float=htb,
caption={[Usage of the ARC Echo client.]
         \textbf{Usage of the Arc echo client.\textcolor{white}{hmf}}}]
$ arcecho http://localhost:60000/Echo text
[ text ]
\end{lstlisting}

In this example, the server and the client are running on the same computer such that the hostname \textit{localhost} can be utilized. 
For debugging it is advisable to check the logfile which was assigned inside the server configuration file.
It is commonly found at /var/log/arched.log.

>>>>

\subsection{The ARC Echo Web Service}
\label{sec:arc_echo_web_service}

@@

\lstsetARCHEDXML
\lstinputlisting
	[label=lst:arched_arcecho_xml,float=htb,
	caption={[HED configuration file.]
	\textbf{HED configuration file.}}]
{../examples/src/services/arched_arcecho.xml}
The first line of the XML file contains the XML declaration.
Several attributes can be defined here but at least the XML version should be specified.
The configuration as a whole is encapsulated by the element \textit{ArcConfig}. It also performs the setting of namespaces, which are expected to be mostly invariant across all server installations. % ABBREVIATIONS?? - MG
The \textit{Server} element, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as the location of the Pid-file or ofthe Log-file.
The \textit{ModuleManager} holds the \textit{path} to the plugin libraries.
Several paths may be defined here.
Due to the fact that the first library matching the plugin name is loaded, the order is relevant.
The path should be at least assigned to the ARC installation directory.
Otherwise, the set of ARC MCC plugins might not be found.
The next elements are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the names of the dynamic libraries within the path defined in the \textit{ModuleManager}.
Finally, the chain, which creates the layered structure, is declared within the element \textit{Chain}.
It is composed of the elements \textit{Component}, \textit{Plexer} and \textit{Service}.
Due to a MCC plugin may contain several components, one has to specify more exact which one to load. This is to be done using the \textit{name} attribute i.e. the plugin \textit{mcchttp} realises two components: \textit{http.service} and \textit{http.client}. Since we are defining a configuration file for a service, the \textit{http.service} should be used.
Furthermore the elements may have the attribute \textit{id} as a unique identifier within the file.
Regarding the components and the services a plugin (implemented as a *.so file that is searched in the paths previously specified) has to be loaded which provides the implementation of its functionality. The further configuration depends on the plugin's individual functionality.\\
%
% within the chain ... 3 types of elements
%
%Its needed to distinguish between the plugins and the components.
%The plugins refer to shared libraries that can be integrated as modules with the HED to extend its functionality.
%The Components refer to the implementation of Web Services within any of those libraries.

@@

% $ rm -f /var/log/arc/arched.log
% $ tail -n100 -f /var/log/arc/arched.log
%...
%$ killall arched
%
%
The name of the program is followed by the parameter \textit{-c}.
The string following that argument contains the path to the configuration file.
Once the server is running, the client can be used as described in Listing~\ref{lst:arcecho_client_invokation}.
\lstsetKSH
\begin{lstlisting}[
label=lst:arcecho_client_invokation,float=htb,
caption={[Usage of the ARC Echo client.]
         \textbf{Usage of the Arc echo client.\textcolor{white}{hmf}}}]
$ arcecho http://localhost:60000/Echo text
[ text ]
\end{lstlisting}

In this example, the server and the client are running on the same computer such that the hostname \textit{localhost} can be utilized. 
For debugging it is advisable to check the logfile which was assigned inside the server configuration file.
It is commonly found at /var/log/arc/arched.log.

### 2010-09-20 doc/tutorials/ws-programming-tutorial/doc/tex_timeservice/timeservice.tex
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/

In order to start the service, the \textit{arched} command, shown in Listing~\ref{lst:arched_timeservice_ksh}, has to be used.
It is recommended to examine the log file \textit{/var/log/arched.log} if the server configuration file has been modified to  assert the start was successful.

>>>>

In order to start the service, the \textit{arched} command, shown in Listing~\ref{lst:arched_timeservice_ksh}, has to be used.
It is recommended to examine the log file \textit{/var/log/arc/arched.log} if the server configuration file has been modified to  assert the start was successful.
